NHF1 General Read Sequence Figure Generation

### 2022-06-13 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Changes to axis bounds

>>>>

```{r CPD_mismatch_anchored_nucleotide_frequencies_filtered, fig.width = 11, fig.height = 8}
min3PrimeCutSiteDistance = 1
max3PrimeCutSiteDistance = 12

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                               minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                               minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
```

### 2022-06-13 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Changes to axis bounds

>>>>

```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 9}
minReadLength = 18
plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"), minReadLength = minReadLength)
plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"), minReadLength = minReadLength)

plotSequenceFrequencies(CPDCGASeqFreq$rep1,
                        title = "CPD CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"), minReadLength = minReadLength)
plotSequenceFrequencies(CPDCGASeqFreq$rep2,
                        title = "CPD CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"), minReadLength = minReadLength)
```
